\documentclass[11pt]{wrceletter}


\name{Dennis Evangelista}
\position{Assistant Professor}
%\email{\href{mailto:evangeli@usna.edu}{\emph{evangeli@usna.edu}}}
\email{evangeli@usna.edu}
\telephone{410-293-6132}

\date{\today}

\usepackage{designature}
\signature{\vspace*{-0.625in}\includesignature\\Dennis Evangelista\\Ph.D.~Integrative Biology, UC Berkeley}
%\signature{Dennis Evangelista\\Assistant Professor} % title not needed if in letterhead
\address{\null} %{105 Maryland Avenue\\Annapolis, MD 21402} % leave blank, provided in letterhead
%\longindentation=0in % to change signature to be flushleft

\begin{document}
\begin{letter}{% recipient address here
}

% opening here
\opening{To the Admissions Committee:}
\raggedright % if you like this sort of thing
\setlength{\parindent}{15pt} % if you like this sort of thing

This letter of recommendation is for MIDN 2/C Amar S Viswanathan, who has applied to your medical program. I was Mr.~Viswanathan's instructor in ES200 (Introduction to Systems Engineering) and EW202 (Principles of Mechatronics). Mr Viswanathan is an excellent candidate and I am happy to recommend him to your program. 

In engineering work, Mr.~Viswanathan picked up concepts very quickly and was able to integrate apply ideas from multiple areas to produce useful applications. He worked well on design teams that developed both hardware and software, and even worked in his medical interests into a colonoscopy video game and questions about robotic surgery and application of machine learning to studies of molecular pathways. 

I am a biologist by training and my research areas are in comparative biomechanics. In this regard, Mr.~Viswanathan compares favorably with biology undergraduates I have seen at MIT, Harvard, Berkeley, and UNC. Mr.~Viswanathan has assisted in biomedical research projects on humans here at USNA, including the effect of body shape on physical readiness test (PRT) performance -- which has led to changes in the way the entire US Navy does the PRT; and studies of cognitive performance during physically maximal performance. LT Middleton, who supervised the former study, states, ``he was an asset to my research team, and I am impressed with his ability to rapidly assimilate, master, and apply new information.'' My colleague Prof.~Jaramillo, who supervised the latter study, notes ``[Viswanathan] was not just a subject but could easily run the experiment from beginning to end. He learned how to obtain, analyze and interpret EEG data from the study and was always eager to learn and active taking initiatives. A very inquisitive midshipman and I have no doubt he will excel in his medical studies.'' 

I typically advise my pre-med undergrads to shadow a physician, which I undersand Mr.~Viswanathan has done under a surgeon and a urologist.

Besides such factors that are typical for overachiever pre-meds like Mr.~Viswanathan, I believe physicians who are cross trained in engineering fields have great potential for medical technology development. In addition, as a Naval Academy midshipman, Mr.~Viswanathan has had intensive leadership training; our current circumstances tell me we need strong, scientifically capable leaders who understand biology and medicine, who are motivated to assume higher responsibilities of command, citizenship, and government, with the integrity to speak truth to power. 

\closing{Very respectfully,} % provides empty 

%\ps{post script here}
%\encl{enclosure here}
\end{letter}
\end{document}







%Good Morning Sir,
%
%Here is a CV that I updated this morning. I'd like you to specifically speak to my contributions to a classroom environment (asking questions, contributing to class discussion, etc.), as well as teamwork capabilities (like in labs or projects). I think I've also demonstrated my ability to learn and grasp engineering disciplines and studies very quickly, and I think you should speak to that as well. Also, speak to any characteristics or personality traits you have observed while mentoring me in finding projects to work on or attempts to combine my engineering education with my passion for medicine. Please let me know if you have any questions, or if I am being too vague. Thank you.
%Very Respectfully,
%
%A.S.Viswanathan
%MIDN          USN

%- picking up concepts in ES200 and EW202 very quickly
%- applying concepts from other classes and coursework to matters in ES200/EW202, demonstrating ability to integrate and apply concepts from multiple different areas for useful applications
%- team building (team projects had good grades and good cultures/attitudes)
%- trying to draw connections and adapt engineering concepts to medicine (colonoscopy game), asking questions about robotic medicine and robotic surgery
%- doing biomedical research (assisted 2 studies the first was about the effect of anthropomorphic dimensions (body shape) on sit-up performance (done with LT Middleton) and the EEG exhaustion study (done with 1/C Skinner and Prof Cienfuegos)
%- teaching others (tutoring in almost all coursework, my company mates frequently rely on me to explain challenging STEM Concepts, explaining our engineering coursework to my neighbors in class, doing MGSP
%- contributing to classroom environment (asking questions, drawing parallels to medicine/other concepts)
%- have done a decent amount of medical shadowing (shadowed a general surgeon last summer and a urologist for 2 weeks)
%- volunteering (MIDS 4 Kids, NESA Jamboree)
%
%There’s also stuff on my CV, I tried to meet your requirements the best I could. I apologize for the tardiness I’m on an LREC in Colombia and things have been pretty hectic. Thank you for your patience.
%
%I am surprised MIDN Viswanathan has not asked me for one. MIDN Viswanathan was very instrumental in helping MIDN Skinner's data gathering. He was not just a subject but could easily run the experiment from beginning to end. He learned how to obtain, analyze and interpret EEG data from the study and was always eager to learn and active taking initiatives. A very inquisitive midshipman and I have no doubt he will excel in his medical studies.
%
%
